Paper notes

### 2019-08-22 paper_notes.Rmd
Add files via upload

---
output:
  bookdown::pdf_document2:
    toc: false
 #   keep_tex: false
    fig_caption: yes
title: "Paper notes"
author: Rocco Paolillo
bibliography: "references.bib"
# target: BIGSSS Research Day by September 15th, presented  on October 25th. 6000 words: around 12 pages.
# csl: apa.csl # by default: Chicago style
header-includes:
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{xcolor} 
- \usepackage{amsmath}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.lp="fig:")

install.packages("tinytex", repos = "https://cloud.r-project.org" )

library(knitr)
library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)
# library(kableExtra)
library(dplyr)
library(grid)
library(ggrepel)
library(magicfor)
library(dplyr)
library(plot3D)
library(rgl)
library(plotly)

# Here functions that are used.

# Calculation ethnic utility (for each option)
# i_e: ethnic threshold (ideal point)
# M: right-side decreasing slope
# x: number agents in neighborhood with same color
# n: total number agents in neighborhood
# S: left-side increasing slope
# Note: if (x > n){U <- NA} to show the case number of agents in neighborhood different from 8, so that utility is calculated based on this, although x-axis in graph has 8 points  (excluded from calculation)

 #  f_eth <- function(i_e,M,x,n,S){
  #   if (x > n){
  #     U <- NA}else{
 #   if (x < round(n*i_e,digits = 2)){
  #    U <- (x / round((n*i_e),digits = 2)) * S
 #      }else {
 #      U <- M + ((1- (x/n))*(1-M))/(1-i_e)   
  #    }
#     round(U,digits = 2)
 #      }
#   }

@@

# Calculation value utility (for each option)

@@

# Probability (random utility with logistic regression) to relocate

prob <- function(d_u_e,d_u_v,e_w,v_w){round(1 / (1 + exp(-(e_w*k)*(d_u_e) + (-(v_w*k)*(d_u_v)))),digits= 2)}

# install.packages("tinytex", repos = "https://cloud.r-project.org" ) if debug needed?

@@

# f2 <- function(p,M,x,n,S)

@@

# name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)
# plot(num_sim_col,Utility_T, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)
# report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_T)
# print(report_E)

# func_type <- c(rep("symmetric",9),rep("constant",9),rep("threshold",9))

@@

# symmetric
# constant
# threshold

@@

# f_val <- function(e_w,ew_ng,M,i_v,S)

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S <- 0
M <- 0 #M can be either 0 or 1, M = 0 is for declining slope, M = 1 keeps utility = 1 for values out of range, so S = 0 keeps  the threshold  with values out of the distance equal 0
# M regulates the right side of the slope, S the left side of the slope

@@

# funct_symm_v <- c(rep("symmetric",9),rep("threshold",9))

@@

thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Threshold Schelling (S=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))

# symm_val_plot
# thres_val_plot

@@

Ethnic utility, separating ethnic_weight and ideal payoff for ethnicity (i_e) -> based on ethnicity of agents (color)
The ethnic weight follows the beta distribution, *maybe* report Blitzstein 4 beta cases, and anyway considering ethnic_weight and value_weight are complementary

Specify n > x <- U:NA in formula

```{r heatmap-log,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}

# to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility

d_u_e <-  magic_result_as_vector()
d_u_v <- rep(seq(-1,1,by = 0.1),21) 
e_w <- 0
v_w <- 1-e_w
k <- 10

df <- data.frame(d_u_e,d_u_v,e_w,v_w)

title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))

 plot_fina_rast <-  suppressWarnings(suppressMessages(
    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff. ethnic (alternative - current)",y = "Diff. value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5)) 
    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
  ))

 fx <- d_u_e
 fy <- d_u_v
 fz <- ass$prap

 # persp(x = seq(-1, 1, by = 0.1),
   #   y = seq(-1, 1, by = 0.1),
   #   fz)

  d <- plot3d(fx,fy,fz,col="blue")
  rgl.postscript("d.eps",fmt="eps")

 test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) %>% layout(legend = list(x = 0.1, y = 0.9))
 #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
 #fx

# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)

# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")

#is.data.frame(ass)
#  print(plot_fina_rast)

print(plot_fina_rast)

# knitr::include_graphics("gg.png" )

# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)

@@

```{r heat2,  fig.width=5,fig.height=4,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}

# to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility

d_u_e <-  magic_result_as_vector()
d_u_v <- rep(seq(-1,1,by = 0.1),21) 
e_w <- 0
v_w <- 1-e_w
k <- 10

df <- data.frame(d_u_e,d_u_v,e_w,v_w)

title_cond_fin <- paste0("Ethnic weight = ",e_w*k,"; ","Value weight = ",v_w*k)
ass <- mutate(df, prap = prob(d_u_e, d_u_v,e_w,v_w))
fina_rast <- ggplot(ass,aes(d_u_e,d_u_v))

 plot_fina_rast <-  suppressWarnings(suppressMessages(
    fina_rast + geom_raster(aes(fill = prap)) + theme_bw() + labs(x = "Diff. ethnic (alternative - current)",y = "Diff. value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5)) 
    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability")
  ))

 fx <- d_u_e
 fy <- d_u_v
 fz <- ass$prap

 # persp(x = seq(-1, 1, by = 0.1),
   #   y = seq(-1, 1, by = 0.1),
   #   fz)

#  d <- plot3d(fx,fy,fz,col="blue")
#  rgl.postscript("d.eps",fmt="eps")

 test_trida <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", mode="markers", color=fz) 
 #p <- export(p = last_plot(),file = "plotly.png", selenium = NULL)
 #fx

# test_trid <- plot3d(df_3$a,df_3$b,df_3$C)

# plotly_IMAGE(test_trida, width = 500, height = 500, format = "png", scale = 2, out_file = "test.png")

#is.data.frame(ass)
#  print(plot_fina_rast)

print(test_trida)
print(plot_fina_rast)

# knitr::include_graphics("gg.png" )

# plot3d(fx,fy,fz, col = "blue",xlab = "eth",ylab="val",zlab="prob", type = "s",size = 2)

@@

```{r logistic,  fig.width=4,fig.height=3, fig.align="center", include=TRUE, echo=FALSE}

# to add: -1 for MIN. Utility Alternative, +1 for MAX Alternative Utility

e_w <- 0.6
v_w <- 1 - e_w
k <- 10

# d_u_e <- -1

dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w)
dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w)
dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w)
dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w)
dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w)
dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w)
dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w)
dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w)
dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w)
dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w)
dis_0   <- prob(d_u_e,0.0,e_w,v_w)
dis_0.1 <- prob(d_u_e,0.1,e_w,v_w)
dis_0.2 <- prob(d_u_e,0.2,e_w,v_w)
dis_0.3 <- prob(d_u_e,0.3,e_w,v_w)
dis_0.4 <- prob(d_u_e,0.4,e_w,v_w)
dis_0.5 <- prob(d_u_e,0.5,e_w,v_w)
dis_0.6 <- prob(d_u_e,0.6,e_w,v_w)
dis_0.7 <- prob(d_u_e,0.7,e_w,v_w)
dis_0.8 <- prob(d_u_e,0.8,e_w,v_w)
dis_0.9 <- prob(d_u_e,0.9,e_w,v_w)
dis_1   <- prob(d_u_e,1.0,e_w,v_w)

  value_difference <- seq(-1.0,1.0, by = 0.1)
#  prob_relocation <- seq(0.0, 1.0,  by = 0.1)

  title_cond_prob <- paste0("PROB ALT","Diff eth = ",d_u_e,"Ew = ",e_w*10,"Vw = ",v_w*10)

 final_prob <-  suppressWarnings(suppressMessages(
    plot_report_prob + geom_point() + theme_bw() + labs(x = "DIFF VAL",y = "Probability") + ggtitle(label = title_cond_prob) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted") 
  ))

  print(final_prob)

```{r ethnic utility individual-run,fig.width=4,fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE}

# f2 <- function(p,M,x,n,S)

i_e = 0.2
S = 0
M = 1
n = 6

f0m <- f_eth(i_e,M,0,n,S)
f1m <- f_eth(i_e,M,1,n,S)
f2m <- f_eth(i_e,M,2,n,S)
f3m <- f_eth(i_e,M,3,n,S)
f4m <- f_eth(i_e,M,4,n,S)
f5m <- f_eth(i_e,M,5,n,S)
f6m <- f_eth(i_e,M,6,n,S)
f7m <- f_eth(i_e,M,7,n,S)
f8m <- f_eth(i_e,M,8,n,S)

# num_sim_col <- seq(0, 8, by = 1)
Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
# name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)

# plot(num_sim_col,Utility_E, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility",  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)

#report_E <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similar ethnics neighborhood j = ", seq(0, 8, by = 1), "; Utility ij = ", Utility_E)

@@

knitr::kable(report_E,align="c") # much better printed visualization

@@

```{r value individual run,fig.width=5,fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE }

e_w <- 0.4
i_v <- 0.2
S  <- 1
M <- 0 #S regulates the left side of the slope, M the right side

fv0d2 <- f_val(e_w,0,M,i_v,S)
fv1d2 <- f_val(e_w,0.1,M,i_v,S)
fv2d2 <- f_val(e_w,0.2,M,i_v,S)
fv3d2 <- f_val(e_w,0.3,M,i_v,S)
fv4d2 <- f_val(e_w,0.4,M,i_v,S)
fv5d2 <- f_val(e_w,0.5,M,i_v,S)
fv6d2 <- f_val(e_w,0.6,M,i_v,S)
fv7d2 <- f_val(e_w,0.7,M,i_v,S)
fv8d2 <- f_val(e_w,0.8,M,i_v,S)
fv9d2 <- f_val(e_w,0.9,M,i_v,S)
fv10d2 <- f_val(e_w,1.0,M,i_v,S)

# name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)

mean_ew_ng <- seq(0.0, 1.0, by = 0.1)
ew_agent <- rep(e_w,11)
Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)
Mv <- rep(M,11)
Sv <- rep(S,11)
des_dist <- rep(i_v,11)

@@

title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M = ",M,"S = ",S)

@@

# plot(value_mean_neighborhood,Utility_V, xlab = "Mean ethnic weight neighborhood j", ylab = "Value Utility neighborhood j",  main = "Value Utility for neighborhood j of agent i",  sub = name_V)

# report_v <- paste0(name_V,"; Mean ethnic weight j = ", seq(0.0, 1.0, by = 0.1), "; Utility ij = ", Utility_V)

knitr::kable(report_V,align="c") # much better printed visualization

# print(final_v)
# print(final_repV)

@@

```{r ANNEX - ethnic_multiple_run, moore neighborhood, include=TRUE, echo=FALSE}

# f2 <- function(p,M,x,n,S)

#i_e = 0.5
M = 0
S = 1
n = 8

for (i_e in seq (0.0,1.0, by = 0.1)){

f0m <- f_eth(i_e,M,0,n,S)
f1m <- f_eth(i_e,M,1,n,S)
f2m <- f_eth(i_e,M,2,n,S)
f3m <- f_eth(i_e,M,3,n,S)
f4m <- f_eth(i_e,M,4,n,S)
f5m <- f_eth(i_e,M,5,n,S)
f6m <- f_eth(i_e,M,6,n,S)
f7m <- f_eth(i_e,M,7,n,S)
f8m <- f_eth(i_e,M,8,n,S)

#num_sim_col <- seq(0, n, by = 1)
Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)
#name_E <- paste0("Desired proportion i = ",i_e,"; M = ",M,"; S = ",S)

#plot(num_sim_col,Utility_Es, xlab = "Similar ethnics neighborhood j", ylab = "Ethnic Utility", ylim = c(0,1),xlim = c(0,n),  main = "Ethnic Utility for neighborhood j of agent i",  sub = name_E)

#report_Es <- paste0("M = ",M,"; S = ",S,"; Desired proportion i = ",i_e,"; Similars in j= ", seq(0, n, by = 1), "; Utility ij = ", Utility_Es)

#print(report_Es)

final_E <- suppressWarnings(suppressMessages(
plot_report_E + geom_point() + theme_bw() + labs(x = "Number similar agents in j",y = "Ethnic Utility j") + ggtitle(label = title_cond) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(0,n), breaks = seq(0,n,by = 1)) 
))

final_repE <- knitr::kable(report_E,align="c") # much better printed visualization

print(final_E)
print(final_repE)

}
```

Value utility, based on agents' desired distance (i_v) between the agent's ethnic_weight (e_w) and neighborhood's average ethnic_weight (calculated out of agents residing there)
Calculate ethnic weight average of neighborhoods with n agents > 0.

 **check:** Explain how S and M vary for the constant function, the comment seems lost

```{r ANNEX- value_similarity, echo=FALSE }

i_v <- 0.1
S  <- 1
M <- 0 #different values  of M do change results, even for M < 1

for (e_w in seq (0.0,1.0, by = 0.1)){

fv0d2 <- f_val(e_w,0,M,i_v,S)
fv1d2 <- f_val(e_w,0.1,M,i_v,S)
fv2d2 <- f_val(e_w,0.2,M,i_v,S)
fv3d2 <- f_val(e_w,0.3,M,i_v,S)
fv4d2 <- f_val(e_w,0.4,M,i_v,S)
fv5d2 <- f_val(e_w,0.5,M,i_v,S)
fv6d2 <- f_val(e_w,0.6,M,i_v,S)
fv7d2 <- f_val(e_w,0.7,M,i_v,S)
fv8d2 <- f_val(e_w,0.8,M,i_v,S)
fv9d2 <- f_val(e_w,0.9,M,i_v,S)
fv10d2 <- f_val(e_w,1.0,M,i_v,S)

# name_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"; M = ",M,"; S = ",S)

>>>>

---
output:
  bookdown::pdf_document2:
    toc: false
 #   keep_tex: false
    fig_caption: yes
title: "Paper notes"
author: Rocco Paolillo
bibliography: "references.bib"
always_allow_html: yes
# target: BIGSSS Research Day by September 15th, presented  on October 25th. 6000 words: around 12 pages.
# csl: apa.csl # by default: Chicago style
header-includes:
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{xcolor} 
- \usepackage{amsmath}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.lp="fig:",warning = FALSE)

# install.packages("tinytex", repos = "https://cloud.r-project.org" )

library(knitr)
library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)
library(dplyr)
library(grid)
library(ggrepel)
library(magicfor)
library(dplyr)
library(plot3D)
library(rgl)
library(plotly)
library(tidyr)
library(plyr)
library(rgl)
library(graphics)
library(cowplot)
library(magick) 
library(xtable)

# Calculation ethnic utility

@@

# Calculation value utility

@@

# ethnic utility difference and value utility difference

d_u_e <-  magic_result_as_vector()
d_u_v <- rep(seq(-1,1,by = 0.1),21)

dfprob <- data.frame(d_u_e,d_u_v,e_w=0,v_w=0,k=0)

dfprob
# Probability to move to alternative (random utility with logistic regression)

prob <- function(d_u_e,d_u_v,e_w,v_w,k){round(1 / (1 + exp((-(e_w*k)*(d_u_e)) + (-(v_w*k)*(d_u_v)))),digits= 2)}

prob_3d <- function(b){
  fx <- d_u_e
  fy <- d_u_v
  fz <- b$prob

  tit <- paste0("Ethnic weight = ",b$e_w*b$k,"; ","Value weight = ",b$v_w*b$k, "\n\r -1:MIN Alternative, 1:MAX Alternative")

   tridi_prob <- plot_ly(x=fx,y=fy,z=fz, type="scatter3d", color=fz, mode="markers")  %>% 
    layout(scene = list(
       xaxis = list(title = "x = Diff. Ethnic Ut."),
       yaxis = list(title = "y = Diff. Value Ut."),
       zaxis = list(title = "z = Probability")
     ), 
     annotations = (list(x = 0.5, y = 1, text = tit, showarrow = F, font=list(size=18)
     ))
   ) %>% hide_colorbar()

 tridi_prob

# install.packages("tinytex", repos = "https://cloud.r-project.org" ), try if debug needed

@@

@@

@@

@@

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S <- 0
M <- 0

@@

@@

thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Threshold Schelling (S=0,M=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))

@@

$$
P_j=\frac{1}{1 + \exp((-ew\cdot k\times \Delta_{U_e})+(-vw\cdot k \times \Delta_{U_v}))}
$$

Where:\par
- $P_j$: Probability to relocate to alternative neighborhood \textit{j} leaving the current neighborhood
- $ew$:  Ethnic weight of agent \textit{i}
- $\Delta_{U_e}$: Ethnic Utility Difference (alternative - current)
- $vw$: Value weight \textit{i}
- $\Delta_{U_e}$: Value Utility Difference (alternative - current)
- $k$: constant

The idea of $k$ constant is to include the parameter of determinism in the random utility formula, i.e. from 0: the probabiity to choose the alternative is totally random due to random term $\epsilon$, to infinity, the best option is taken with probability equal to 1. To reduce the number of parameters, and being constitent with the conceptual model, I derive the parameter for ethnic utility from the ethnic weight $ew$ and the parameter for value utility from the value weight $vw$ in the agent-based  model. Remember that $ew$ ranges $[0,1]$ according to beta distribution, and $vw$ is calculated as $1-ew$. The parameter is calculated as $k\cdot ew$ and $k \cdot vw$, meaning that with $k=10$, the parameter for ethnic utility will range from 0 to 10, $k=100$, range from 0 to 100, $k = 0$: all agents will have parameter equal 0. It will be one slider in the agent-based model.\par
The aim of the logistic function above is to implement the random  utility for a binary choice for the agent between the current location $x$ and alternative location $j$, with $P_{xj}=0$ meaning the agent stays on the current location, $P_{xj}=1$ the agent moves to the alternative location $j$.\par
Below I report some graphs on $P_{xj}$ where the logistic funtion above is implemented for each combination of ethnic utility difference $\Delta_{U_e}$ and value utility difference $\Delta_{U_v}$. These are the possible values expected from the agent-based model: assuming that both the ethnic and value utility for each location ranges from 0 to 1, the difference (alternative - current) ranges from -1 (alternative = 0, current = 1), to 1 (alternative =1, current = 0), with 0 meaning equal utility sizes. This creates 11 levels  for each utility, $\times$ 2 number of utility = 441 conditions. The aim of the graphs was to relate the probability as function of 2 dimensions, so I use the heatmaps in fig.\ref{fig:heatmaps}. They have the same content of the 3D plots in fig.\ref{fig:prob3D} which I think serve better the scope: in the R code you can interact with the graph and see actual probability for each point, but need to do it from the RStudio interface (chunk "interact3d").\par
Each graph reports the parameter ethnic weight $ew \cdot k$ and parameter value weight $vw \cdot k$. In all conditions $k = 10$, which I saw shows most realistic scenarios, i.e. lower probability for lower ethnic/utility difference. To check if the random utility for binary choice is correctly implemented, $P_{xj}=0.50$ with $ew \cdot k = 0$ and $vw \cdot k = 0$, meaning the choice between current and alternative location is totally random. In the last condition $ew \cdot k = 100$ and $vw \cdot k = 100$, $P_{xj}=0$ for all conditions where current location is higher in both types of utility (below the diagonal), shifts to $P_{xj}=1$ for all conditions with both utilities higher in the alternative location (above the diagonal), and $P_{xj}=0.5$ on the diagonal where the alternatives have same utility with difference equal 0. So the choice is totally dependent on the characteristic of the neighborhood, with the best option being taken. I think it can confirm the random utility framework for two options.

```{r heatmaps,  fig.width=12,fig.height=12,fig.cap="Probability to choose alternative location",fig.align="center", include=TRUE, echo=FALSE}

k_v <- 10

df_0 <- mutate(dfprob,e_w=0,v_w=0,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))
df_05 <- mutate(dfprob,e_w=0.5,v_w=0.5,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))
df_maxe <- mutate(dfprob,e_w=1,v_w=0,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))
df_maxv <- mutate(dfprob,e_w=0,v_w=1,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))
df_r <- mutate(dfprob,e_w=0.1,v_w=0.1,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))
df_1 <- mutate(dfprob,e_w=10,v_w=10,k=k_v, proba = prob(d_u_e, d_u_v,e_w,v_w,k))

prob_comb <- function(a){
title_cond_fin <- paste0("Ethnic weight = ",a$e_w*a$k,"; ","Value weight = ",a$v_w*a$k)
fina_rast <- ggplot(a,aes(d_u_e,d_u_v))

 plot_fina_rast <-  suppressWarnings(suppressMessages(
    fina_rast + geom_raster(aes(fill = proba)) + theme_bw() + labs(x = "Diff. ethnic (alternative - current)",y = "Diff. value (alternative - current)") + labs(title = title_cond_fin, caption = "-1: Min Utility Alternative; 1: Max Utility Alternative") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust=0.5),plot.caption = element_text(hjust=0.5)) 
    + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0, colour = "red", linetype = "dotted") + scale_fill_continuous(name = "Probability",limits=c(0,1), breaks=seq(0,1,0.25))
  ))
}

plot_0 <- prob_comb(df_0)
plot_05 <- prob_comb(df_05)
plot_maxe <- prob_comb(df_maxe)
plot_maxv <- prob_comb(df_maxv)
plot_r <- prob_comb(df_r)
plot_1 <- prob_comb(df_1)

grid.arrange( plot_0,plot_05,plot_maxe,plot_maxv,plot_r,  plot_1,nrow=3,ncol=2)

@@

```{r prob3D,  fig.width=18,fig.height=18,fig.cap="Probability to choose alternative location 3D",fig.align="center", include=TRUE, echo=FALSE}

tridi_0_0 <- ggdraw() + draw_image("3d_0_0.png")
tridi_5_5 <- ggdraw() + draw_image("3d_5_5.png")
tridi_10_0 <- ggdraw() + draw_image("3d_10_0.png")
tridi_0_10 <- ggdraw() + draw_image("3d_0_10.png")
tridi_100_100 <- ggdraw() + draw_image("3d_100_100.png")
tridi_1_1 <- ggdraw() + draw_image("3d_1_1.png")

grid.arrange(tridi_0_0,tridi_5_5,tridi_10_0,tridi_0_10,tridi_1_1,tridi_100_100,ncol=2,nrow=3)

@@

```{r interact3D, include=TRUE,echo= FALSE}

# To explore the 3D graph, select all lines and run (alt + Enter), or change in line above r interact3D, include = TRUE

prob_3d(df_0)
prob_3d(df_05)
prob_3d(df_maxe)
prob_3d(df_maxv)
prob_3d(df_1)
prob_3d(df_r)

#Plotly seems more adapted for html, but works here
```

```{r ethnic utility individual-run,fig.width=4,fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE}
# ETHNIC UTILITY:
# Choose parameters for desired ethnic similar proportion (i_e, float number), left-slope utility curve (S),right-slope utility curve (M),total number of agents in the neighborhood (n), then run (green arrow top-right).
# The calculations are done for a max=8 neighbors (assuming we keep 8-patches Moore neighbor in NetLogo). Utility can be calculated with n > 8, but table row and x-axis graph will stop at 8.

i_e = 0.5   # parameters to manipulate
S = 0     # Symmetric single-peaked function: S=1,M=0
M = 0     # Linear + Constant function = S=1,M=1
n = 8     # Schelling Threshold function = S=0,M=1

f0m <- f_eth(i_e,M,0,n,S) # ethnic utility for each option, the increasing number is the number of agents of same ethnicity
f1m <- f_eth(i_e,M,1,n,S)
f2m <- f_eth(i_e,M,2,n,S)
f3m <- f_eth(i_e,M,3,n,S)
f4m <- f_eth(i_e,M,4,n,S)
f5m <- f_eth(i_e,M,5,n,S)
f6m <- f_eth(i_e,M,6,n,S)
f7m <- f_eth(i_e,M,7,n,S)
f8m <- f_eth(i_e,M,8,n,S)

Utility_E <- c(f0m,f1m,f2m,f3m,f4m,f5m,f6m,f7m,f8m)    # used to make up table and graph

@@

suppressWarnings(suppressMessages(
knitr::kable(report_E,align="c")
))

@@

```{r value individual run,fig.width=5, fig.height= 3, fig.align="center", fig.pos="H", include=TRUE, echo=FALSE }
# VALUE UTILITY:
# Choose parameters for ethnic weight of agent i (e_w), desired value distance (i_v), left-slope utility curve (S),right-slope utility curve (M).
# The calculations are done for each ethnic weight mean of the neighborhood, from 0 to 1. The extreme case is desired value distance 1, meaning all mean ethnic weight of the neighborhood are included. Values of i_v > 1 would not affect results, but nonsense

e_w <- 0.4    # parameters to manipulate
i_v <- 0
S  <- 0
M <- 0

fv0d2 <- f_val(e_w,0,M,i_v,S)      # value utility for each option, the increasing number is the ethnic weight of neighborhood j
fv1d2 <- f_val(e_w,0.1,M,i_v,S)
fv2d2 <- f_val(e_w,0.2,M,i_v,S)
fv3d2 <- f_val(e_w,0.3,M,i_v,S)
fv4d2 <- f_val(e_w,0.4,M,i_v,S)
fv5d2 <- f_val(e_w,0.5,M,i_v,S)
fv6d2 <- f_val(e_w,0.6,M,i_v,S)
fv7d2 <- f_val(e_w,0.7,M,i_v,S)
fv8d2 <- f_val(e_w,0.8,M,i_v,S)
fv9d2 <- f_val(e_w,0.9,M,i_v,S)
fv10d2 <- f_val(e_w,1.0,M,i_v,S)

Utility_V <- c(fv0d2,fv1d2,fv2d2,fv3d2,fv4d2,fv5d2,fv6d2,fv7d2,fv8d2,fv9d2,fv10d2)  # used to make up table and graph

mean_ew_ng <- seq(0.0, 1.0, by = 0.1)
ew_agent <- rep(e_w,11)
Mv <- rep(M,11)
Sv <- rep(S,11)
des_dist <- rep(i_v,11)

@@

title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M =", M,"; ", "S = ",S)

@@

suppressWarnings(suppressMessages(
knitr::kable(report_V,align = "c")
))

@@

```{r logistic, fig.width=5,fig.height=4,fig.align='left',include=TRUE, echo=FALSE}

magic_for()

e_w <- 0.5
v_w <- 0.5
k <- 10

dis_1neg   <- prob(d_u_e,-1.0,e_w,v_w,k)
dis_0.9neg <- prob(d_u_e,-0.9,e_w,v_w,k)
dis_0.8neg <- prob(d_u_e,-0.8,e_w,v_w,k)
dis_0.7neg <- prob(d_u_e,-0.7,e_w,v_w,k)
dis_0.6neg <- prob(d_u_e,-0.6,e_w,v_w,k)
dis_0.5neg <- prob(d_u_e,-0.5,e_w,v_w,k)
dis_0.4neg <- prob(d_u_e,-0.4,e_w,v_w,k)
dis_0.3neg <- prob(d_u_e,-0.3,e_w,v_w,k)
dis_0.2neg <- prob(d_u_e,-0.2,e_w,v_w,k)
dis_0.1neg <- prob(d_u_e,-0.1,e_w,v_w,k)
dis_0   <- prob(d_u_e,0.0,e_w,v_w,k)
dis_0.1 <- prob(d_u_e,0.1,e_w,v_w,k)
dis_0.2 <- prob(d_u_e,0.2,e_w,v_w,k)
dis_0.3 <- prob(d_u_e,0.3,e_w,v_w,k)
dis_0.4 <- prob(d_u_e,0.4,e_w,v_w,k)
dis_0.5 <- prob(d_u_e,0.5,e_w,v_w,k)
dis_0.6 <- prob(d_u_e,0.6,e_w,v_w,k)
dis_0.7 <- prob(d_u_e,0.7,e_w,v_w,k)
dis_0.8 <- prob(d_u_e,0.8,e_w,v_w,k)
dis_0.9 <- prob(d_u_e,0.9,e_w,v_w,k)
dis_1   <- prob(d_u_e,1.0,e_w,v_w,k)

  value_difference <- seq(-1.0,1.0, by = 0.1)

  title_cond_prob <- paste0("Diff. Ethnic Utility (alternative - current): ",d_u_e)
  title_caption <-  paste0("Ethnic weight = ",e_w*10," ; ","Value weight = ",v_w*10
                           ,"\n\r","-1: Min Utility Alternative; 1: Max Utility Alternative"
                           )

 final_prob <-  suppressWarnings(suppressMessages(
    plot_report_prob + geom_point() + theme_bw() + labs(x = "Diff. Value Utility (alternative - current)",y = "Probability") +
      labs(title=title_cond_prob, caption = title_caption)

      + theme(plot.title = element_text(hjust = 0.5),plot.caption = element_text(hjust=0.5)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25)) + scale_x_continuous(limits =  c(-1,1), breaks = seq(-1,1,by = 0.2)) + geom_vline(xintercept = 0, colour = "red", linetype = "dotted") + geom_hline(yintercept = 0.5, colour = "red", linetype = "dotted") 
  ))

  plot(final_prob)
